iPre: A Cross-platform Mobile App\\for Image Classification

### 2017-03-31 document/paper.tex
document roughly done

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

@@

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The abstract goes here.
\end{abstract}

@@

Researchers have demonstrated steady progress in computer vision by validating their work against ImageNet -- an academic benchmark for computer vision. Successive models continue to show improvements, each time achieving a new state-of-the-art result: QuocNet, AlexNet, Inception (GoogLeNet), BN-Inception-v2. At the meantime, Python libraries for numerical computation in the field of machine learning have been developed, such as TensorFlow and Theano. Keras is a high-level neural networks API, written in Python and capable of running on top of either TensorFlow or Theano. It was developed with a focus on enabling fast experimentation. There are many trained image classification models for Keras, such as VGG16, VGG19, ResNet50, and Inception v3.

iPre, is a mobile app for image classification using Keras library with VGG16\cite{vgg16} model. It behaves like a photo album. After registering an account, users can log in and upload their images. All the uploaded images would appear at main page. Clicking one of them, users would see predicted classifications of that image, presented in a pie chart, a bar chart and a probability table. All the images and their predictions are stored permanently, so users can always log back in and browse their images.

@@

\section{APP Demo}

@@

\section{Conclusion}
The conclusion goes here.

@@

% use section* for acknowledgment
\section*{Acknowledgment}

The authors would like to thank...

@@

@@

>>>>

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  \usepackage{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

\usepackage{booktabs}

@@

\makeatletter
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Image Classification has been studied and developed for years. Machine learning models continue to show improvements on classification results. To explore more practical usage of these work, the paper describes the development of a cross-platform mobile app, called iPre, which runs in Android phones and web browsers. Part \rom{1} describes the background, and introduces iPre, which follows a web development pattern and uses services from Amazon Web Services. Part \rom{2} describes the structure of the app, from frontend to backend, with server support, Android development, and classification model. Part \rom{3} demonstrates the app on an Android device. Part \rom{4} demonstrates the app on a Chrome browser. Part \rom{5} concludes the work.
\end{abstract}

@@

Researchers have demonstrated steady progress in computer vision by validating their work against ImageNet -- an academic benchmark for computer vision. Successive models continue to show improvements, each time achieving a new state-of-the-art result: QuocNet, AlexNet, Inception (GoogLeNet), BN-Inception-v2. At the meantime, Python libraries for numerical computation in the field of machine learning have been developed, such as TensorFlow and Theano. Keras is a high-level neural networks API, written in Python and capable of running on top of either TensorFlow or Theano. It was developed with a focus on enabling fast experimentation. There are many trained image classification models for Keras, such as VGG16\cite{vgg16}, VGG19, ResNet50\cite{resnet}, and Inception v3\cite{inception}.

iPre, is a mobile app for image classification using Keras library with VGG16 model. It behaves like a photo album. After registering an account, users can log in and upload their images. All the uploaded images would appear at main page. Clicking one of them, users would see predicted classifications of that image, presented in a pie chart, a bar chart and a probability table. All the images and their predictions are stored permanently, so users can always log back in and browse their images.

@@

\section{Android Demonstration}
To better demonstrate the usage of iPre, this part walks through the functionalities from a user's perspective. It's been installed on Nexus 6, an Android device with API 25.

\subsection{Log In}
Figure \ref{fig:login} shows the log-in page, which allows the user register a new account or log in with an existing username. For demo purpose, a user named 'ece1780' has been created. Several images were already uploaded under this account.

\begin{figure}[h!]
  \centering
  \includegraphics[height=\linewidth]{login.png}
  \caption{Log in.}
  \label{fig:login}
\end{figure}

\subsection{Main Page}
Figure \ref{fig:main} shows the main page, including an photo album, which lists all the images of the user 'ece1780'. The user can scroll and browse the images. There is a collapse button at top right corner. After clicking it, the user can choose to upload a new image, or log out current account.

\begin{figure}[h!]
  \centering
  \includegraphics[height=\linewidth]{main.png}
  \caption{Main page.}
  \label{fig:main}
\end{figure}

\subsection{Classification}
If we choose an image from album in main page, iPre would lead us to classification page. Figure \ref{fig:view1} and figure \ref{fig:view2} shows us an example (bottom right corner image from album). There are three presentations of classification results, including a pie chart, a bar chart, and a table. Each presentation shows us five values of probability.

\begin{figure}[h!]
  \centering
  \includegraphics[height=\linewidth]{view1.png}
  \caption{View page.}
  \label{fig:view1}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[height=\linewidth]{view2.png}
  \caption{View page.}
  \label{fig:view2}
\end{figure}

\section{Browser Demonstration}
Since it's built through a web development approach, it doesn't need to be confined to any specific platform. Figure \ref{fig:pc_login}, \ref{fig:pc_main} and \ref{fig:pc_view} show a web version of the app, which runs on a Chrome browser.

\begin{figure}[h!]
  \centering
  \includegraphics[width=\linewidth]{pc_login.png}
  \caption{Log in.}
  \label{fig:pc_login}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=\linewidth]{pc_main.png}
  \caption{Main page.}
  \label{fig:pc_main}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=\linewidth]{pc_view.png}
  \caption{View page.}
  \label{fig:pc_view}
\end{figure}

@@

\section{Conclusion}
The work is related to Image Classification problem, which is the task of assigning an input image one label from a fixed set of categories. This is one of the core problems in Computer Vision that, despite its simplicity, has a large variety of practical applications. Taking advantage of pre-trained neural networks and high-level libraries, iPre classifies images uploaded to user's albums.
It is platform-independent. Following a web development pattern, iPre was designed to be more flexible. It can be run on any browsers, or migrated to native mobile platforms, such as Android, IOS, and Windows Phone.
It's simple to use and user-friendly. It improves user interface by different classification result interpretations, including two charts and a table.
The app is currently running on an EC2 instance of type c4.large. It takes approximately 7 seconds to classify an image right now. Classification time depends on server performance. The better the server performs, the sooner it classifies. As listed in Table \ref{tab:table1}, classification time depends on EC2 instance types.

\begin{table}[h!]
  \centering
  \caption{performance on difference EC2 instance types.}
  \label{tab:table1}
  \begin{tabular}{cccc}
    \toprule
    Model & vCPU & Mem (GiB) & Time (second)\\
    \midrule
    t2.micro & 1 & 1 & 50.42\\
    t2.small & 1 & 2 & 35.87\\
    m3.medium & 1 & 3.75 & 13.25\\
    c4.large & 2 & 3.75 & 7.61\\
    c4.4xlarge & 16 & 30 & 6.12\\
    \bottomrule
  \end{tabular}
\end{table}

@@

% use section* for acknowledgment
%\section*{Acknowledgment}

%The authors would like to thank...

@@

\bibitem{resnet}
He, Kaiming, et al. "Deep residual learning for image recognition." Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2016.

\bibitem{inception}
Szegedy, Christian, et al. "Rethinking the inception architecture for computer vision." Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition. 2016.

@@

\bibitem{wiki:deep}
Chatfield, Ken, Karen Simonyan, Andrea Vedaldi, and Andrew Zisserman. "Return of the devil in the details: Delving deep into convolutional nets." arXiv preprint arXiv:1405.3531 (2014).
